---
title: "Readme"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(quiltr)
library(magrittr)
```

## Quilt

R package to Quilt data package manager. See: https://docs.quiltdata.com/

Extremely experimental - should be considered *totally unusable* right now. This package currently has a hard requirement on Python and access to shell commands.

### Installation

* `devtools::install_github('stillmatic/quiltr')`
* `pip install quilt`
<!-- * `devtools::install_github('apache/spark', ref='master', subdir='R/pkg')` -->

If you have trouble testing in Rstudio, follow [instructions](https://stackoverflow.com/questions/31121645/rstudio-shows-a-different-path-variable) to set the proper PATH for Rstudio.

### Demo

```{r, echo=TRUE}
seattle <- qload("akarve.seattle_911", "responses")
```

```{r, error=FALSE}
seattle %>% head %>% knitr::kable()
```

## Design Philosophy

Given that the bulk of development on the Quilt project is done in Python, it makes sense to provide wrappers to the Python code for non-essential commands, and provide native R code to handle import/export of data only.

Many of the commands named by Quilt conflict with existing R functions, especially in `base`, e.g. `search` or `ls`. To avoid confusion we generally will prefix functions with `q`. 

Known bugs:

* https://github.com/pandas-dev/pandas/pull/9661


## TODO

* [X] search
* [ ] permissions/auth
* [ ] download
* [ ] push
* [X] versioning
* [X] import and retrieve 
