---
title: "Readme"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(quiltr)
library(magrittr)
```

## Quiltr

An R package to Quilt data package manager. See [docs](https://docs.quiltdata.com/) and [GitHub](https://github.com/quiltdata/quilt)

This package is in reasonable shape and covers most of the Quilt Python API. Pull requests, issue reports, and further testing are very welcome.

### Installation

* `devtools::install_github('stillmatic/quiltr')`
* `pip install quilt`
* `pip install git+git://github.com/quiltdata/quilt` - you probably need this

If you have trouble testing in Rstudio, follow [instructions](https://stackoverflow.com/questions/31121645/rstudio-shows-a-different-path-variable) to set the proper PATH for Rstudio.

### Demo

Load data file:

```{r, echo=TRUE}
seattle <- qload("akarve/seattle_911", "responses")
```

```{r, error=FALSE}
seattle %>% head %>% knitr::kable()
```

Create a package:

```{r, echo=FALSE}
readme <- "# Iris Test

## Est nomine aeternum signata pendebat Iuppiter amamus

Lorem markdownum tractu faciles, in haesit parte **tot** immaduisse solis
petiitque; tinguamus! Ista comitatur vobis videat simul ima mille ictu infelix
variarum.

- Pars levat lacerare sinuatus nec vomens gravitate
- Haliumque stabat vultum intravit nam deum
- Proles suo ignibus vidit
- Referre ferrugine laesi ait nymphae matrem loquendo
- Oscula eo pariter

## Primo contendite ramos evocat cervum tulit medicamine

Serpentis meliore tela est: Harpyia albentia. Est odio heros: ordine a Lacinia
fulvo Sisyphon Oeclides ac conatur senserit has. Telas unus siccis pio parere
vitiaverat duc mea Circes primos cruoris Mareoticaque dedit sua nulla coniunx.

## Graves sol deprensi simul

Haec hoc neve ferunt, verba lacrimis penetrabit illic praecipitata. Sustinet dum
nunc procorum herbae terrasque in soporem callidus aethera rotatum **credensque
habet**. Mersitque novitate et populi. Morte da flamma **vetus tuae** velamenta
collige florebat festas.

## Per esse dixit

Imperat nubibus fugiant Maeonia. Ait Nec super gerebam si occidit Priami videor;
non tactu secutae! Simulacraque silvas Cycnum, Orithyian turba, vetaris.

Maior tenet nihil negetur, poena Spartana ardor, prementem primum patremque *ut*
hasta flava, ebur frontem atra, est. Vobis sua, voto, ubi, e rigido. [Cum
cui](http://www.de-oraque.net/coma.aspx): pugna.

Obscenae quas templa aequora consuetissima motis clamant. Sortes solum
praecordiaque rupit accommodat relicta. Et quod [praemia sidera
colebat](http://nam-satis.org/) etiamnum."

data(iris)
```

```{r, eval = F}
qbuild("hua/iris", README.md = readme, iris = iris)
qpush("hua/iris", TRUE)
```

## Design Philosophy

Given that the bulk of development on the Quilt project is done in Python, it makes sense to provide wrappers to the Python code for non-essential commands, and provide native R code to handle import/export of data only. Additionally, the Quilt project is under heavy development; rather than reimplementing this moving target in R, we can use 

Many of the commands named by Quilt conflict with existing R functions, especially in `base`, e.g. `search` or `ls`. To avoid confusion we generally will prefix functions with `q`. 

This package makes extensive use of the R package `reticulate` to interface with Python. The file IO and conversion is done via the `feather` project, in lieu of R support for Apache Arrow (see, e.g. [ARROW-1325](https://issues.apache.org/jira/browse/ARROW-1325) and other stuff on the arrow-dev listserv).
